Continuous Reinforcement Learning

### 2018-06-22 magnitudes.tex

>>>>

This extends to situations with continuous time and continuous or
discrete space, where the state jumps from $s$ to $s'$ with probability $\deltat
L(s,a,s')$ at each time. (Here $L$ is signed, with $L(s,a,s)$ usually
negative to represent the jump from $s$; $L$ is the generator of the
Markov process.) Writing $p_J(s,a,s')$ the law of
$s'$ knowing that a jump has occurred, and $\deltat J(s,a)$ the
probability of jumping, we have $L(s,a,s')=J(s,a)(p_J(s,a,s')-\delta(s))$
and
